Testing the precision of Bangla Communication Scale: Item Response Theory Guided Analysis

### 2022-02-04 manuscript.Rmd
Landscape mode is now corrected

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)

set.seed(123)
par(family = "Arial")
```

@@

## Item Analysis

@@

(ref:facIdFig) Factor Identification Methods (A) Parallel analysis  indicated the optimal number of factors were two. (B) Scree plot suggested One facor. (C) Hull method indicated 1 factors were required to balance the model fit and number of parameters.

@@

@@

```{r item-plots, inclide =F}

iteminfo <- plot(fit, type = "infotrace",which.item =2)

itemplot.01 <- tabledown::ggiteminfo(fit,1,6)+apatheme+
  ggtitle(" Item03")+theme(legend.position = "none")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

itemplot.02 <- tabledown::ggiteminfo(fit,2,6)+apatheme+
  ggtitle(" Item04")+theme(legend.position = "none")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

@@

@@

```{r figconrel, fig.cap = "Conditional Reliability.",  out.height='100%', warning=FALSE}

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: false
    latex_engine: xelatex
    includes:
      in_header: header.tex
mainfont: Arial
---

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600, fig.width = 6,
 fig.asp = 0.8,out.width = "80%", dev=c('png','postscript'))
#options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Arial")
```

@@

## Item Analysis and Exploratory Factor Analysis

@@

(ref:facIdFig) Factor Identification Methods (A) Parallel analysis  indicated the optimal number of factors were two. (B) Scree plot suggested One factor. (C) Hull method indicated one factor were required to balance the model fit and number of parameters.

@@

```{r irttab, results='asis'}
papaja::apa_table(IRT.details, caption = "Items discrimination and response category difficulty thresholds of 17 items in  Bangla Communication Scale (n =581)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
```

@@

```{r Test-info, include =F}

# iteminfo <- plot(fit, type = "infotrace",which.item =2)
# 
# itemplot.01 <- tabledown::ggiteminfo(fit,1,6)+apatheme+
#   ggtitle(" Item03")+theme(legend.position = "none")+
#   labs(y = "Item Information")+
#   scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
#   xlab(expression(theta))+ ylab(expression(I(theta)))
# 
# 
# itemplot.02 <- tabledown::ggiteminfo(fit,2,6)+apatheme+
#   ggtitle(" Item04")+theme(legend.position = "none")+
#   labs(y = "Item Information")+
#   scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
#   xlab(expression(theta))+ ylab(expression(I(theta)))
# 
# 
#

@@

```{r}
# This chinks holds code of compiled item info code created using facet wrap. (Not included in manuscript)
pacman::p_load(reshape,ggsci)
Theta <- matrix(seq(-6,6, by = .1))

##Item Extraction
item03 <- extract.item(fit, 1)#item number
item04 <- extract.item(fit, 2)
item06 <- extract.item(fit, 3)
item07 <- extract.item(fit, 4)
item08 <- extract.item(fit, 5)
item10 <- extract.item(fit,6)
item11<- extract.item(fit, 7)
item12 <-extract.item(fit, 8)
item13 <- extract.item(fit, 9)
item14 <- extract.item(fit, 10)
item15 <- extract.item(fit, 11)
item17 <- extract.item(fit, 12)
item18 <- extract.item(fit, 13)
item19 <- extract.item(fit, 14)
item20 <- extract.item(fit, 15)
item21 <- extract.item(fit, 16)
item22 <- extract.item(fit, 17)

##Item Info
Item03 <- iteminfo(item03, Theta)
Item04 <- iteminfo(item04, Theta)
Item06 <- iteminfo(item06, Theta)
Item07 <- iteminfo(item07, Theta)
Item08 <- iteminfo(item08, Theta)
Item10 <- iteminfo(item10, Theta)
Item11 <- iteminfo(item11, Theta)
Item12 <- iteminfo(item12, Theta)
Item13 <- iteminfo(item13, Theta)
Item14 <- iteminfo(item14, Theta)
Item15 <- iteminfo(item15, Theta)
Item17 <- iteminfo(item17, Theta)
Item18<- iteminfo(item18, Theta)
Item19 <- iteminfo(item19, Theta)
Item20 <- iteminfo(item20, Theta)
Item21 <- iteminfo(item21, Theta)
Item22 <- iteminfo(item22, Theta)

#Data frame

item.info.data <- as.data.frame(cbind(Item03, Item04,Item06, Item07, Item08,
                                      Item10, Item11, Item12, Item13, Item14,
                                      Item15, Item17, Item18, Item19, Item20,
                                      Item21, Item22))

item.info.data.long <- melt(item.info.data)

item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), item.info.data.long)

pacman::p_load(ggsci)

item.info.plot <- ggplot(item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("Item Information Plot")+theme(legend.position = "none")+
  facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+geom_area()+ scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

# facet_wrap(~variable,scales = "free")++geom_hline(yintercept = .20, colour ="red")

ggsave("Figures/itemInfoplot.png",item.info.plot, width = 8, height =8, dpi = 1200, bg ="white")

```{r figIIC, fig.cap = "Item Information Curve.",  out.height='100%',out.width='100%', warning=FALSE}

knitr::include_graphics("Figures/itemInfoplot.png", dpi =600)

@@

```{r figconrel, fig.cap = "Conditional Reliability.", out.width= '100%', out.height='50%', warning=FALSE}
